---
title: "Alcohol vs Seat choice"
author: "Diana Reyes"
date: "September 17, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_O$: There is no difference among the mean amount of alcohol consumed per week by row
$H_A$

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```



## Conclusions

The P value is less than 0.05 which leads to reject the null hypothesis. The boxplots show that people who sit in the back row consume the most alcohol as oppose to people who sit in the front and middle row.
